Intelligent Quadcopter for IARC 2018

### 2018-06-01 IARC_Paper_2018/Paper.tex
Uh we had some things not best in formatting

\section*{Introduction}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, Mission 7 requires novel solutions to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

@@

	\subsection*{Yearly Milestones}

@@

\section*{Air Vehicle}
	\subsection*{Propulsion and Lift System}
			The vehicle utilizes an x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omnidirectional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.

@@

\section*{Payload}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s. In addition, the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.

@@

		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph]

@@

\section*{Operations}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{my_enumerate}
				\item Check battery voltage (12.0-12.6v) and insert
				\item Make sure LiDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{my_enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

\section*{Risk Reduction}
	\subsection*{Vehicle Status}
		\subsubsection*{Shock/Vibration Isolation}
		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure. The team decided that there is no need for extra damping. After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts. The team believes there is no need to have landing shocks, as the sophisticated Arducopter flight stack has logic to recognize landing. Because of this, nominal landings will not interfere with the guidance or navigation of the drone.

@@

\section*{Conclusion}
	Texas Aerial Robotics' solutions to the challenges provided by IARC Mission 7 are bountiful and diverse. The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success. Unique software utilizes input from an expansive collection of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area. Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
	\nocite{redmon2016yolo9000}
	\nocite{GitHubSPACEROBOTICS}
	\nocite{HoughTransform}
	\nocite{CannyEdgeDetection}
	\bibliography{bibliography}
	\bibliographystyle{plain}

>>>>

\section*{INTRODUCTION}
	Previous aerial robotics missions have always allowed for GPS or set navigation points that allowed for constant locational awareness for the drone. Location data is important to any mission, as telemetry prevents various failures, including complete loss of control for the drone. Thus, Mission 7 requires novel solutions to deriving this critical telemetry, as GPS is forbidden. Additionally, the aircraft must be capable of interacting with ground vehicles without being directly informed of their locations, requiring advanced detection and robust hardware designed for repeated contact.

@@

	\pagebreak
	\subsection*{Yearly Milestones}

@@

\section*{AIR VEHICLE}
	\subsection*{Propulsion and Lift System}
			The vehicle utilizes an x-y axis symmetrical quad-rotor system. This provides a balanced airframe optimized for omnidirectional maneuvering. The frame is lifted by four T-Motor U3 KV700 motors. These motors provide 1.8 [kg] of thrust per motor at 100\% throttle when paired with a 4-cell battery and 13 [in] propellers for total 7.2 [kg] of thrust. This is necessary for our 3.15 [kg] weight to maintain a 2.2 thrust-to-weight ratio, ideal for battery life and flight time.

@@

\section*{PAYLOAD}
	The drone has been designed to carry all the necessary GNC sensors, 2D LiDAR, an array of cameras, and 3 Nvidia Jetson TX2s. In addition, the drone carries a telemetry radio, kill switch, and RC receiver in order to carry out safe flight.
	\subsection*{Sensor Suite}
		\subsubsection*{GNC Sensors}
			The quadcopter uses eight sensors for flight control. The main sensors used for the navigation of the quadcopter include a downward-facing 1D LiDAR module, a PX4FLOW optical sensor, and the built-in sensors of the Pixhawk 2 flight control board.

@@

		The eCalc online tool was used to validate our calculations, and as seen by the generated graph below, there should be no issue reaching above 10 minute flight times at speeds below 15 [mph].

@@

\section*{OPERATIONS}
	\subsection*{Flight Preparations}
		\subsubsection*{Checklist}
			\begin{my_enumerate}
				\item Check battery voltage (12.0-12.6V) and insert
				\item Make sure LiDAR and PX4FLOW are not covered
				\item Make sure that ESCs are plugged in to the right pins
				\item Make sure prop guards are secure
				\item Make sure that the props are on in the correct direction (leading edge in)
				\item Make sure that the props are not upside down
				\item Make sure props are clear of any structures
				\item Make sure Kill Switch is in off position
				\item Power on controllers
				\item Make sure TELEM2 is unplugged
				\item Plug in power loop
				\item Turn Kill Switch to on position
				\item Make sure ground station has good telemetry
				\item Verify critical sensors are giving good data
				\item Plug in TELEM2
				\item SSH start/verify autonomous scripts are running
				\item Make sure everyone is clear of drone
				\item Verify mode switch in Stabilize
				\item Hold safety button
				\item Mode switch to Autonomous
			\end{my_enumerate}
	\subsection*{Man/Machine Interface}
		The drone has a DX7 RC controller interface for system checks and emergency situations. In addition, the flight controller can be monitored via a telemetry radio using Mission Planner. Our autonomous scripts must be initiated by an SSH connection to our Nvidia Jetsons.

\section*{RISK REDUCTION}
	\subsection*{Vehicle Status}
		\subsubsection*{Shock/Vibration Isolation}
		The modern Pixhawk flight controller contains internal damping from the vibration of the drone's structure. The team decided that there is no need for extra damping. After completion of our first drone last year, flight logs from the Pixhawk confirmed that vibration on the built quadcopter was well within recommended amounts. The team believes there is no need to have landing shocks, as the sophisticated Arducopter flight stack has logic to recognize landing. Because of this, nominal landings will not interfere with the guidance or navigation of the drone.

@@

\section*{CONCLUSION}
	Texas Aerial Robotics' solutions to the challenges provided by IARC Mission 7 are bountiful and diverse. The physical design process, from the ground up, optimizes flight time while enabling the physical contact required for success. Unique software utilizes input from an expansive collection of sensors to overcome the telemetry limitations imparted by the contest and track the dynamic objectives as they move about the area. Safe operation of these vast networks of interlocking components has been ensured through particular hardware selection and thorough vetting.
	\nocite{redmon2016yolo9000}
	\nocite{GitHubSPACEROBOTICS}
	\nocite{HoughTransform}
	\nocite{CannyEdgeDetection}
	\bibliography{bibliography}
	\bibliographystyle{plain}
